Research

### 2025-10-09 research.qmd
profile update

-   **Topics:** Public policy evaluation on health IT, Digital technologies, Artificial intelligence (AI) for Behavioral Decision-making, Economics of AI
-   **Methodologies:** Applied econometrics, experiments, machine learning, statistical learning

## Work in Progress

@@

1.  **Smartphone Use, Social Support, and Sleep Health.** Shaokang Yang, Idris Adjerid. [SSRN](http://dx.doi.org/10.2139/ssrn.5368531) -- *Under Review at **Information Systems Research***

2.  **Friends over Feeds: How Social Smartphone Use Reduces Screen Time.** Shaokang Yang, Idris Adjerid. -- *In preparation for submission (target: Organization Science)*

3.  **Pet Ownership and Mental Health During the Pandemic: Evidence from an E-Commerce Platform** Li Lin, Shaokang Yang -- *Data collection phase*

@@

1.  **The Abortion War: When Restrictions Meet Technology.** Shaokang Yang, Idris Adjerid. -- *Data collected, working on empirical analysis*

2.  **Pro-Choice Vs Pro-Life: The Impact of Healthcare Digitalization on Infant Health.** -- *Data collected, working on empirical analysis*

@@

1.  **Prevention is Better Than Cure: Artificial Intelligence-based Nudging to Prevent Digital Addiction.** -- *Ideation phase.*

>>>>

-   **Topics:** Artificial intelligence (AI) for Behavioral Decision-making,  Technology policy evaluation, Digital technologies, Economics of AI 
-   **Methodologies:** Applied econometrics, experiments, machine learning, LLM, Causal AI

## Research

@@

1. **Smartphone Use, Social Support, and Sleep Health.** Shaokang Yang, Idris Adjerid. [SSRN](http://dx.doi.org/10.2139/ssrn.5368531) — *Under Review at **Information Systems Research***  
   - Accepted to WISE, Nashville, TN, Dec 17–19, 2025  
   - Accepted to Conference on Health IT and Analytics (CHITA), Washington, DC, May 2024  
   - Presented to Doctoral Consortium of CHITA, Washington, DC, May 2024  
   - Presented to 33rd Annual POMS Conference, Orlando, FL, May 2023  
   - Accepted to CHITA, Washington, DC, May 2023

2. **Friends over Feeds: How Social Smartphone Use Reduces Screen Time.** Shaokang Yang, Idris Adjerid. — *In preparation for submission (target: **Organization Science**)*  
   - Scheduled at INFORMS, Atlanta, GA, Oct 28, 2025  
   - Accepted to CHITA, Austin, TX, Apr 2025  
   - Presented at INFORMS Annual Meeting, Seattle, WA, Oct 2024

3. **Pet Ownership and Mental Health During the Pandemic: Evidence from an E-Commerce Platform.** Li Lin, Shaokang Yang. — *Data collection phase*

---

@@

1. **The Abortion War: When Restrictions Meet Technology.** Shaokang Yang, Idris Adjerid. — *Data collected, working on empirical analysis*  
2. **Pro-Choice Vs Pro-Life: The Impact of Healthcare Digitalization on Infant Mortality.** Shaokang Yang. — *Data collected, working on empirical analysis*

---

@@

1. **Prevention is Better Than Cure: Artificial Intelligence-based Nudging to Prevent Digital Addiction.** — *Ideation phase*
